\documentclass[a4paper]{article}

\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
\usepackage[margin=0.75in]{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{array}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

\titleformat{\section}{\scshape \Large}{}{0em}{}[\titlerule]
\pagestyle{empty}

\newcommand{\TwoRowSubheading}[4]{
  \item \begin{tabular*}{.95\textwidth}{@{}l @{\extracolsep{\fill}} r@{}}
    \textbf{#1} & \textbf{#2} \\
    {\color{gray}#3} & {\itshape #4} \\
  \end{tabular*}
}

\begin{document}

% HEADER
\begin{tabular*}{\textwidth}{@{}l @{\extracolsep{\fill}} r@{}}
 \Huge \textsc{Sean W. Evans} &
 \href{mailto:Sean@SeanWEvans.com}{E-Mail} \ \faEnvelopeO \\
 \faPhone\ \href{tel:15163302517}{+1 (516) 330-2517}  &
 \href{https://github.com/SeanWEvans}{Github} \ \faGithub \\
 \faHome\ \href{https://SeanWEvans.com}{SeanWEvans.com} & 
 \href{https://www.linkedin.com/in/sean-evans-49398229b}{Linked In} \ \faLinkedinSquare
\end{tabular*}

% SUMMARY
\section{Summary}
Systems-level engineer with 6+ years building end-to-end ML, vision, and document-analysis pipelines, plus experience in C/C++/CUDA, runtime systems, Postgres tooling, and mathematical modeling. I specialize in rapid prototyping across abstraction layers (theory → GPU → product), automating complex workflows, and shipping high-reliability systems at scale.

% SKILLS
\section{Skills}
\begin{itemize}[leftmargin=*,label=]
    \item \textbf{Languages:} Python, C, C++, CUDA, C\#, Perl, SQL (PostgreSQL/T-SQL)
    \item \textbf{Machine Learning:} PyTorch, TensorFlow, Detectron2, CNN/RNN OCR, NLP (SpaCy)
    \item \textbf{Computer Vision:} OpenCV, document segmentation, structural analysis
    \item \textbf{Systems \& Performance:} Linux, Git, Make/CMake, multiprocessing, GPU kernels
    \item \textbf{Data \& SDKs:} PostgreSQL, XML (DOM/SAX), PDF libraries, MS Office SDK, Adobe SDK
    \item \textbf{Scientific \& Typesetting:} \LaTeX, MathJax, numerical \& geometric modeling
\end{itemize}

% EXPERIENCE 
\section{Experience}
\begin{itemize}[leftmargin=*,label=]

\TwoRowSubheading
{Data Conversion Laboratory}
{Remote}
{Machine Learning Engineer}
{May 2021 -- Feb 2025}

\begin{itemize}[leftmargin=1em,rightmargin=1em,label=]
    \item \textbf{Designed} and deployed a Detectron2-based document segmentation model (equations, tables, figures) achieving industry-comparable accuracy and reducing manual classification by \textbf{50\%}.
    \item \textbf{Built} a CNN–RNN equation OCR engine (Torch7/Lua) converting images to \LaTeX{} with near state-of-the-art accuracy in production.
    \item \textbf{Automated} large-scale document styling with NLP + MS Office SDK, reducing a recurring 40-hour manual workload to \textbf{under 2 hours}.
    \item \textbf{Implemented} a robust OpenCV checkbox detection pipeline (>96\% accuracy) handling rotation, noise, and thousands of formatting variants.
    \item \textbf{Developed} high-throughput processing systems capable of millions of pages/week across OCR, normalization, and structural analysis.
\end{itemize}

\TwoRowSubheading
{Data Conversion Laboratory}
{Remote}
{Software Engineer}
{Sep 2020 -- May 2021}

\begin{itemize}[leftmargin=1em,rightmargin=1em,label=]
    \item \textbf{Built} a scalable PDF cleaning + OCR preprocessing system (deskew, despeckle, rotate) processing \textbf{100k+ pages/week/server}.
    \item \textbf{Authored} automated \LaTeX{} correction and JATS XML tooling replacing a full-time manual process with a reliable automated pipeline.
    \item \textbf{Developed} a comprehensive .docx → XML converter via MS Office InterOp, normalizing heterogeneous client inputs into a unified representation.
    \item \textbf{Applied} TDD, Agile workflows, and robust XML parsing (DOM/SAX) to ship reliable, production-grade tools.
\end{itemize}

\TwoRowSubheading
{Data Conversion Laboratory}
{Queens, NY}
{Lead Technology Analyst}
{Sep 2019 -- Sep 2020}

\begin{itemize}[leftmargin=1em,rightmargin=1em,label=]
    \item \textbf{Led} optimization initiatives across ingest, transformation, and QA pipelines; mentored junior developers; served as technical stakeholder liaison.
\end{itemize}

\TwoRowSubheading
{Data Conversion Laboratory}
{Queens, NY}
{Technology Analyst}
{May 2018 -- Sep 2019}

\begin{itemize}[leftmargin=1em,rightmargin=1em,label=]
    \item \textbf{Built} custom data conversion and document-normalization utilities used in large-scale document migration projects.
    \item \textbf{Maintained} and enhanced high-volume production pipelines supporting multiple enterprise clients.
\end{itemize}

\end{itemize}

% EDUCATION
\section{Education}
\begin{itemize}[leftmargin=*]    
\TwoRowSubheading
{Long Island University}
{Long Island, NY}
{Bachelor of Science in Mathematics}
{2003--2026}
\end{itemize}

\end{document}
